\textbf{Political Instability and Financial Markets}

### 2017-02-13 doc/paper.tex
Code for protest regression table

\begin{table}[!ht]
\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
 & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
  \hline
Protest & 0.282 & 2.113*** & 1.961*** & 1.148*** \\
   & (0.781) & (0.648) & (0.643) & (0.385) \\
  Emerging Market &  &  & 0.216* &  \\
  Index &  &  & (0.129) &  \\
  \hline
  Event Fixed Effect? & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\
  Observations & \multicolumn{1}{c}{3537} & \multicolumn{1}{c}{3537} & \multicolumn{1}{c}{2676} & \multicolumn{1}{c}{3537} \\
  Events & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{11} \\
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors clustered by event are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively.
\end{threeparttable}
\end{center}
\end{table}

>>>>

\begin{table}[!ht]
\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
 & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
  \hline
\ExpandableInput{../tables/protest-regtable.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors clustered by event are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively.
\end{threeparttable}
\end{center}
\end{table}
